### 2019-06-08 2-Chapters/3-Chapter/chapter3.tex
Done for proof reading chapter 4

With this numerical framework, simulations can run on a single CPU or a multi-core machine using joblib \cite{joblib} (see Appendix~\ref{sub:3:parallelSimulations}),
and summary plots are automatically saved as high-quality PNG, PDF and EPS, using matplotlib \cite{matplotlib} and seaborn \cite{seaborn}.
Raw data from each simulation is also saved in a HDF5 file using h5py \cite{h5py}, an efficient and compressed binary format, to allow easy post-mortem exploration of simulation results.
Making new simulations is very easy, one only needs to write a configuration script (\texttt{configuration.py}), without needing a complete knowledge of the internal code architecture.

@@

Simulations are easily executed, \eg, this snippet shows how to start $N=1000$ repetitions of a simple non-Bayesian Bernoulli-distributed problem, for $K=9$ arms, an horizon of $T=10000$ and on $4$ CPUs.
It takes about $20$ min, on a $4$-core $64$-bit GNU/Linux laptop.
Environment variables (\texttt{N=1000} etc) in the command line are not required, but they are convenient.

@@

This library is written in Python \cite{python}, for versions 2.7+ or 3.4+, using \texttt{matplotlib} \cite{matplotlib} for 2D plotting, \texttt{numpy} \cite{numpy} for data storing, random number generations and operations on arrays, \texttt{scipy} \cite{scipy} for statistical and special functions, and \texttt{seaborn} \cite{seaborn} for pretty plotting and colorblind-aware colormaps.

@@

\paragraph{Read the Docs.}
Since $2017$, we have been using the free web service provided by Read the Docs (\href{https://readthedocs.org/}{\texttt{ReadTheDocs.org}}).
Read the Docs allows to automatically build the documentation after every commit. This allows to regularly check that the library is well formatted and can be imported correctly, as well as keeping the online documentation up-to-date.
Moreover, they offer to host the documentation online, at \href{https://smpybandits.rtfd.io/}{\texttt{SMPyBandits.ReadTheDocs.io}}.
For more details, see \href{https://readthedocs.org/projects/smpybandits/}{\texttt{ReadTheDocs.org/projects/SMPyBandits}}.
%
Since its first use, the service did about 180 builds, and about $10\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.readthedocs.yml} file in SMPyBandits main folder, and it builds the documentation in about two minutes.
I have also been building the documentation manually on a weekly basis, to also host it on \href{https://smpybandits.github.io/}{\texttt{SMPyBandits.GitHub.io}} thanks to GitHub pages.
In the last two years, the documentation saw about 8500 unique visits, while the GitHub project have been visited about 3500 unique visits.

\paragraph{Travis CI.}
Since $2018$, we use the free web service provided by Travis CI (\href{https://travis-ci.org/}{\texttt{Travis-CI.org}}).
Travis CI allows to automatically run short numerical simulations after every commit.
This allows to check that each modification on any part of the codebase does not break anything, as well as giving an up-to-date example of log files that shows online the results of different examples of experiments. The tests covers all the main models and almost all the algorithms implemented in SMPyBandits, and it has been proven very useful to quickly find and fix new bugs.
For more details, see \href{https://travis-ci.org/SMPyBandits/SMPyBandits}{\texttt{Travis-CI.org/SMPyBandits/SMPyBandits}}.
%
Since its first use, the service did about 160 builds, and about $30\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.travis.yml} file in SMPyBandits main folder, and it runs numerical experiments with a short horizon (\eg, $T=100$ or $T=1000$) and a small number of repetitions (\ie, $N=4$), but covering all the different models implemented by SMPyBandits (and even including some that are not covered in this chapter, like the Markov model, or the sparse multi-player model).
Builds typically run for $15$ minutes, and Travis CI have been proven to be very useful in our development process.

@@

In this section, we use the SMPyBandits library to compare experimentally various state-of-the-art single-player algorithms on some multi-armed bandit problems.
First, we detail the list of different algorithms that we compare, and the different problems on which they are all tested.
We give the results of the numerical experiments, in terms of mean regret at the end of the experiment of different horizons $T$.
Additional results in terms of real measurements of time and memory are given and discussed in the next Section~\ref{sec:3:timeAndMemoryCosts}.
%
Finally, we give some observations on the results, and the main take-away message of this section is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}
    \item
    \UCB{} is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored.
\end{itemize}

@@

    \item
    %  Algorithm 3 is
    $\mathrm{Exp}3^{++}$ from \cite{Seldin17}, using $\alpha=3$ and $\beta=256$ as advised (\texttt{Exp3PlusPlus}).
    It is a recent variant of the $\mathrm{Exp3}$ algorithm, using an adaptive tuning of its parameter. It is anytime, and was proven to obtain good ``best of both world'' performances, meaning that it achieves $\cO(K\log(T)/\Delta^2)$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.

@@

    \item
    %  Algorithm 9 is
    BESA (Best Empirical Sampled Average) from \cite{Baransi2014},
    % , and it consists in trying to fix a simple observation.
    % For instance in \UCB, if arm $1$ has $100$ samples and arm $2$ has $50$ samples, it should make more sense to only use $50$ samples of arm $1$ to compute and compare any statistics for each arm (\eg, mean).
    % The BESA algorithm for $K=2$ arms is then very simple: at each time step, if arms $1$ and $2$ have $n_1$ and $n_2$ samples, and if $n_1>n_2$ (for instance), first it sub-samples $n_2$ observations from $n_1$, then it computes the mean of these observations, and play the arm maximizing this mean (now that there is the same number of observations for both arms, it makes more sense to compare these quantities).
    % It was analyzed partially for the two-armed case, and the authors illustrated that it can be very efficient empirically.
    % Analyzing it in the generic case was found to be difficult, and is still an open problem.
    which is implemented with a binary tournament, written in a naive but efficient way
    (\ie, not using recursive functions, by using the \texttt{BESA} class with \texttt{''non\_recursive''=True}).
    But the extension to $K>2$ arms is still costly in terms of both time and memory, as illustrated below, and blows-up exponentially  when $K$ increases.
\end{enumerate}

@@

\paragraph{Two different problems.}

We consider two different problems, that are described here for a generic value of $K \geq 2$ the number of arms.
For simplicity, we focus on Bernoulli distributed arms, even if similar results were observed for other distributions, in particular for truncated or untruncated Gaussian distributions.

\begin{itemize}
    \item \textbf{Problem 1} considers $K$ arms of equally spaced means, in $[0,1]$.
    It uses a minimum mean of $0.05$ and a maximum mean of $0.95$.
    For instance, for $K=2$, $\bm{\mu}=[0.05, 0.95]$ and for $K=5$, $\bm{\mu} = [0.05, 0.275, 0.5, 0.725, 0.95]$.

    \item \textbf{Problem 2} takes another approach. Instead of simulating $1000$ times the same problem, it generates a new random problem for each independent run.
    It considers a randomly generated vector of means, each being sampled uniformly at random in $[0,1]$, with a minimum gap of $\Delta^{\min}$, $\bm{\mu} \sim \cE(\Delta^{\min},\mu_{\min},\mu_{\max})$, as well as minimum and maximum values of $\mu_{\min}$ and $\mu_{\max}$.
    This space $\cE_{\Delta^{\min}}$ is defined as $\{ \bm{\mu} \in [\mu_{\min}, \mu_{\max}]^K : \min_{k\neq k'} |\mu_k - \mu_{k'}| \geq \Delta^{\min} \}$.
    We use $\mu_{\min} = \Delta^{\min}$ and $\mu_{\max} = 1 - \Delta^{\min}$,
    and the value used for $\Delta^{\min}$ is $0.1$ for $K \leq 3$ (for ``easy'' problems), and $\frac{1}{3 K}$ for $K \geq 5$ (for ``harder'' problems).
    % 0.1 if NB_ARMS <= 5 else 1. / (3 * NB_ARMS)
\end{itemize}

@@

% WARNING
% \paragraph{Remark.}
We want to conclude by highlighting that a significant amount of time during my PhD was devoted to the development of SMPyBandits, and as such the library, its documentation and this chapter  are considered an important contribution of this thesis.
%
Our library is used for the numerical simulations in all this thesis, except Chapter~\ref{chapter:4}.
% We use it to compare state-of-the-art single-player algorithms designed for stationary MAB in Chapter~\ref{chapter:2}, for multi-armed problems in Chapter~\ref{chapter:5} and for piece-wise stationary problems in Chapter~\ref{chapter:6}.
We also used it in other publications not included in this thesis, like our work on doubling tricks \cite{Besson2018DoublingTricks} that we shortly present in Appendix~\ref{app:2:DoublingTricks}.

\paragraph{Future works.}
%
An interesting future work left on our library SMPyBandits could be to implement variants of the single-player stochastic models, as well as variants for the multi-player or the non-stationary cases.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
For instance it would be interesting to extend the library for problems with non-finite arms, \eg, linear or contextual bandit (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
or to add support for the ``dynamic case'' of multi-player bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
%
At the end of Chapter~\ref{chapter:5}, we present many extensions of the multi-player bandit model,
and even if some have already been implemented, a major future work is to implement the most interesting ones
(tickets \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}).\\
%
\indent
Since $2017$, I also received by email or by GitHub issues some requests to implement new features or models. Most of them were implemented quickly, but some would require more time and are left as possible future works.
Two example of requests include a model where the number of arm can change at some or all time step (an example of such model is called ``sleeping bandit'', \href{https://github.com/SMPyBandits/SMPyBandits/issues/123}{issue 123}), to implement the model of rotting bandits (\href{https://github.com/SMPyBandits/SMPyBandits/issues/156}{issue 156}), or to add a web-based user interface for an even easier usage of the library requiring no command line or knowledge of Python (\href{https://github.com/SMPyBandits/SMPyBandits/issues/133}{issue 133}).

@@

    \item
    % Algorithm 13 is
    Anytime variant of KL-UCB-Switch from \cite{GarivierHadiji2018},
    is a very recent variant of the \klUCB{} algorithm \cite{KLUCBJournal}
    (\texttt{klUCBswitchAnytime}).
    It mimics the \klUCB{} algorithm but uses a much more complicated function to compute the upper confidence bounds, and uses more storage.
    It is anytime, and was prove to obtain good ``best of both world'' performances, meaning that it achieves an asymptotically optimal $\cO(\log(T))$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.
    Empirically, it usually outperforms \klUCB{} in terms of regret, and costs about the same memory, but it is slower.

@@

    \item
    % Algorithm 16 is
    $\mathrm{PHE}$ (Perturbed-History Exploration) from \cite{KvetonSzepesvari2019}, using a perturbation scale of $0.5$ as advised (\texttt{PHE}).
    The algorithm adds $\cO(t)$ \iid{} pseudo-rewards to its history in round $t$, and then pulls the arm with the highest estimated value in its perturbed history.
    It was also analyzed and found to be comparable with \UCB.
    Like $\mathrm{RCB}$, $\mathrm{PHE}$ was found to be empirically slightly worse than other state-of-the-art algorithms.
    Interestingly, its time and memory consumption stay constant with respect to the step number $t$ and the horizon $T$, because generating and summing $t$ pseudo-rewards from a Bernoulli distribution can actually be done in $\cO(1)$ time and space, by using efficient sampling methods for sampling from Binomial distributions.
\end{enumerate}

>>>>

With this numerical framework, simulations can run on a single CPU or a multi-core machine using joblib \cite{joblib} (see Appendix~\ref{sub:3:parallelSimulations}),
and summary plots are automatically saved as high-quality PNG, PDF and EPS, using matplotlib \cite{matplotlib} and seaborn \cite{seaborn}.
Raw data from each simulation is also saved in an HDF5 file, using h5py \cite{h5py}, an efficient and compressed binary format, to allow easy post-mortem manipulation of any simulation results.
Making new simulations is very easy, one only needs to write a configuration script (\texttt{configuration.py}), without needing a complete knowledge of the internal code architecture.

@@

Simulations are easily executed, \eg, Listing~\ref{lst:3:howToRunBasicLibrary} shows how to start $N=1000$ repetitions of a simple non-Bayesian Bernoulli-distributed problem, for $K=9$ arms, an horizon of $T=10000$ and on $4$ CPUs.
It takes about $20$ min, on a $4$-core $64$-bit GNU/Linux laptop.
Environment variables (\texttt{N=1000} etc) in the command line are not required, but they are convenient.

@@

This library is written in Python \cite{python}, for versions 2.7+ or 3.4+, using \texttt{matplotlib} \cite{matplotlib} for 2D plotting, \texttt{numpy} \cite{numpy} for data storing, random number generations and operations on arrays, \texttt{scipy} \cite{scipy} for statistical and special functions, and \texttt{seaborn} \cite{seaborn} for clean plotting and colorblind-aware colormaps.

@@

\textbf{Read the Docs.}
Since $2017$, we have been using the free web service provided by Read the Docs (\href{https://readthedocs.org/}{\texttt{ReadTheDocs.org}}).
Read the Docs allows to automatically build the documentation after every commit. This allows to regularly check that the library is well formatted and can be imported correctly, as well as keeping the online documentation up-to-date.
Moreover, they offer to host the documentation online, at \href{https://smpybandits.rtfd.io/}{\texttt{SMPyBandits.ReadTheDocs.io}}.
For more details, see \href{https://readthedocs.org/projects/smpybandits/}{\texttt{ReadTheDocs.org/projects/SMPyBandits}}.
%
Since its first use, the service did about 180 builds, and about $10\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.readthedocs.yml} file in SMPyBandits main folder, and it builds the documentation in about two minutes.
I have also been building the documentation manually on a weekly basis, to also host it on \href{https://smpybandits.github.io/}{\texttt{SMPyBandits.GitHub.io}} thanks to GitHub pages.
In the last two years, the documentation saw about 8500 unique visits, while the GitHub project have been visited about 3500 unique visits.

\textbf{Travis CI.}
Since $2018$, we use the free web service provided by Travis CI (\href{https://travis-ci.org/}{\texttt{Travis-CI.org}}).
Travis CI allows to automatically run short numerical simulations after every commit.
This allows to check that each modification on any part of the codebase does not break anything, as well as giving an up-to-date example of log files that shows online the results of different examples of experiments. The tests covers all the main models and almost all the algorithms implemented in SMPyBandits, and it has been proven very useful to quickly find and fix new bugs.
For more details, see \href{https://travis-ci.org/SMPyBandits/SMPyBandits}{\texttt{Travis-CI.org/SMPyBandits/SMPyBandits}}.
%
Since its first use, the service did about 160 builds, and about $30\%$ of them were useful to detect newly introduced issues or bugs in the code.
The build is configured using the \texttt{.travis.yml} file in SMPyBandits main folder, and it runs numerical experiments with a short horizon (\eg, $T=100$ or $T=1000$) and a small number of repetitions (\ie, $N=4$), but covering all the different models implemented by SMPyBandits (and even including some that are not covered in this chapter, like the Markov model, or the sparse multi-player model).
Builds typically run for $15$ minutes, and Travis CI have been proven to be very useful in our development process.

@@

In this section, we use the SMPyBandits library to compare experimentally various state-of-the-art single-player algorithms on some multi-armed bandit problems.
First, we detail the list of different algorithms that we compare, and the different problems on which they are all tested.
We give the results of the numerical experiments, in terms of mean regret at the end of the experiment of different horizons $T$.
Additional results in terms of real measurements of time and memory are given and discussed in the next Section~\ref{sec:3:timeAndMemoryCosts}.

Finally, we give some observations on the results, and the main take-away message of this section is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}
    \item
    \UCB{} is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored.
\end{itemize}

@@

    \item
    %  Algorithm 3 is
    $\mathrm{Exp}3^{++}$ from \cite{Seldin17}, using $\alpha=3$ and $\beta=256$ as advised (\texttt{Exp3PlusPlus}).
    It is a recent anytime variant of the $\mathrm{Exp3}$ algorithm, which was proven to obtain good ``best of both world'' performances, meaning that it achieves $\cO(K\log(T)/\Delta^2)$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.

@@

    \item
    %  Algorithm 9 is
    BESA (Best Empirical Sampled Average) from \cite{Baransi2014},
    % , and it consists in trying to fix a simple observation.
    % For instance in \UCB, if arm $1$ has $100$ samples and arm $2$ has $50$ samples, it should make more sense to only use $50$ samples of arm $1$ to compute and compare any statistics for each arm (\eg, mean).
    % The BESA algorithm for $K=2$ arms is then very simple: at each time step, if arms $1$ and $2$ have $n_1$ and $n_2$ samples, and if $n_1>n_2$ (for instance), first it sub-samples $n_2$ observations from $n_1$, then it computes the mean of these observations, and play the arm maximizing this mean (now that there is the same number of observations for both arms, it makes more sense to compare these quantities).
    % It was analyzed partially for the two-armed case, and the authors illustrated that it can be very efficient empirically.
    % Analyzing it in the generic case was found to be difficult, and is still an open problem.
    which is implemented with a binary tournament, written in a naive but efficient way
    (\ie, not using recursive functions, by using the \texttt{BESA} class with the \texttt{''non\_recursive''=True} option).
    But the extension to $K>2$ arms is still costly in terms of both time and memory, as illustrated below, and blows-up exponentially  when $K$ increases.
\end{enumerate}

@@

\paragraph{Two different problems.}
%
We consider two different problems, that are described here for a generic value of $K \geq 2$ the number of arms.
For simplicity, we focus on Bernoulli distributed arms, even if similar results were observed for other distributions, in particular for truncated or untruncated Gaussian distributions.

% \begin{itemize}
    % \item
    \textbf{Problem 1} considers $K$ arms of equally spaced means, in $[0,1]$.
    It uses a minimum mean of $0.05$ and a maximum mean of $0.95$.
    For instance, for $K=2$, $\bm{\mu}=[0.05, 0.95]$ and for $K=5$, $\bm{\mu} = [0.05, 0.275, 0.5, 0.725, 0.95]$.

    % \item
    \textbf{Problem 2} takes another approach. Instead of simulating $1000$ times the same problem, it generates a new random problem for each independent run.
    It considers a randomly generated vector of means, each being sampled uniformly at random in $[0,1]$, with a minimum gap of $\Delta^{\min}$, $\bm{\mu} \sim \cE(\Delta^{\min},\mu_{\min},\mu_{\max})$, as well as minimum and maximum values of $\mu_{\min}$ and $\mu_{\max}$.
    This space $\cE_{\Delta^{\min}}$ is defined as $\{ \bm{\mu} \in [\mu_{\min}, \mu_{\max}]^K : \min_{k\neq k'} |\mu_k - \mu_{k'}| \geq \Delta^{\min} \}$.
    We use $\mu_{\min} = \Delta^{\min}$ and $\mu_{\max} = 1 - \Delta^{\min}$,
    and the value used for $\Delta^{\min}$ is $0.1$ for $K \leq 3$ (for ``easy'' problems), and $\frac{1}{3 K}$ for $K \geq 5$ (for ``harder'' problems).
    % 0.1 if NB_ARMS <= 5 else 1. / (3 * NB_ARMS)
% \end{itemize}

@@

% WARNING
% \paragraph{Remark.}
We want to conclude by highlighting that a significant amount of time during my PhD was devoted to the development of SMPyBandits, and as such the library, its documentation and this chapter  are considered an important contribution of this thesis.
%
Our library is used for the numerical simulations in all this thesis, except Chapter~\ref{chapter:4}.
% We use it to compare state-of-the-art single-player algorithms designed for stationary MAB in Chapter~\ref{chapter:2}, for multi-armed problems in Chapter~\ref{chapter:5} and for piece-wise stationary problems in Chapter~\ref{chapter:6}.
We also used it in other publications not included in this thesis, like our work on doubling tricks \cite{Besson2018DoublingTricks} (see Appendix~\ref{app:2:DoublingTricks}).

\paragraph{Future works.}
%
An interesting future work left on our library SMPyBandits could be to implement variants of the single-player stochastic models, as well as variants for the multi-player or the non-stationary cases.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits /SMPyBandits/issues/}}.
For instance it would be interesting to extend the library for problems with non-finite arms, \eg, linear or contextual bandit (\href{https://github.com/SMPyBandits/SMPyBandits/issues/117}{ticket 117}),
or to add support for the ``dynamic case'' of multi-player bandits to allow arrivals or departures of players (\href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{ticket 124}).
%
At the end of Chapter~\ref{chapter:5}, we present many extensions of the multi-player bandit model,
and even if some have already been implemented, a major future work is to implement the most interesting ones
(tickets \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}).\\
%
\indent
Since $2017$, I also received by emails or by GitHub issues some requests to implement new features or models. Most of them were implemented quickly, but some would require more time and are left as possible future works.
Two example of requests include a model where the number of arm can change at some or all time step (an example of such model is called ``sleeping bandit'', \href{https://github.com/SMPyBandits/SMPyBandits/issues/123}{issue 123}), to implement the model of rotting bandits (\href{https://github.com/SMPyBandits/SMPyBandits/issues/156}{issue 156}), or to add a web-based user interface for an even easier usage of the library requiring no command line or knowledge of Python (\href{https://github.com/SMPyBandits/SMPyBandits/issues/133}{issue 133}).

@@

    \item
    % Algorithm 13 is
    Anytime variant of KL-UCB-Switch from \cite{GarivierHadiji2018},
    is a very recent variant of the \klUCB{} algorithm \cite{KLUCBJournal}
    (\texttt{klUCBswitchAnytime}).
    It mimics the \klUCB{} algorithm but uses a much more complicated function to compute the upper confidence bounds, and uses more storage.
    It is anytime, and was prove to obtain good ``best of both world'' performances, meaning that it achieves an asymptotically optimal $\cO(\log(T))$ regret for problem-dependent bounds, and $\cO(\sqrt{KT})$ for problem-independent bounds.
    Empirically, it usually outperforms (slightly) \klUCB{} in terms of regret, and costs about the same memory, but it is slower.

@@

    \item
    % Algorithm 16 is
    $\mathrm{PHE}$ (Perturbed-History Exploration) from \cite{KvetonSzepesvari2019}, using a perturbation scale of $0.5$ as advised (\texttt{PHE}).
    The algorithm adds $\cO(t)$ \iid{} pseudo-rewards to its history in round $t$, and then pulls the arm with the highest estimated value in its perturbed history.
    It was also analyzed and found to be comparable with \UCB.
    Like $\mathrm{RCB}$, $\mathrm{PHE}$ was found to be empirically slightly worse than other state-of-the-art algorithms.
    Interestingly, its time and memory consumption stay constant with respect to the step number $t$ and the horizon $T$, because generating and summing $t$ pseudo-rewards from a Bernoulli distribution can actually be done in $\cO(1)$ time and space, by using efficient sampling methods for sampling from a Binomial distribution.
\end{enumerate}
